
\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}

\definecolor{maincolor}{HTML}{2E86C1}
\hypersetup{
    colorlinks=true,
    urlcolor=maincolor,
    linkcolor=maincolor
}

\titleformat{\section}{\large\bfseries\color{maincolor}}{}{0em}{}
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[ -- ]
\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Md Rifath Hassan}} \\
    \vspace{2mm}
    Address: Federal Territory of Kuala Lumpur, Malaysia \\
    \href{mailto:mhrifath92@gmail.com}{Email: mhrifath92@gmail.com} \\
    \href{tel:+60104225051}{Mobile/WhatsApp: +60104225051} \\
    \href{https://www.linkedin.com/in/md-rifath-hassan/}{linkedin.com/in/md-rifath-hassan/} \quad
    \href{https://github.com/MHRifathcoders}{github.com/MHRifathcoders} \\
    \vspace{1mm}
\end{center}

\section*{Professional Summary}
Detail-oriented Backend Developer with hands-on experience in building scalable and secure web applications and APIs using Python frameworks like the Django Rest Framework and FastAPI. Proven ability to design and implement robust RESTful services and manage code versioning with Git. Strong knowledge of relational databases and API best practices, with a focus on performance and clean code architecture.

\section*{Core Skills}
\begin{tabbing}
\hspace{3cm} \= \kill
\textbf{Backend} :\> Python, Django, Django Rest Framework, FastAPI \\
\textbf{Web Technologies}: RESTful API, JSON, HTML/CSS  \\
\textbf{Version Control:} \> Git, GitHub \\
\textbf{Databases:} \> PostgreSQL, MySQL, SQLite \\
\textbf{Tools:} \> Docker (basic), Postman, VS Code \\
\textbf{Others:} \> Unit Testing, API Documentation (Swagger/Open-API) \\
 \\
\end{tabbing}

\section*{Professional Experience}
\subsection*{Part Time Backend Developer | Innovative Skills BD, Remote}
\textit{March 2025 – Present} \\

\begin{itemize}
    \item Developed and maintained RESTful APIs for various web applications using Django Rest Framework and FastAPI
    \item Built secure user authentication systems with JWT and session-based login
    \item Integrated third-party APIs for payments, location services, and messaging
    \item Used Git for version control and collaborated on GitHub with teams 
    \item Wrote clean, reusable code and performed unit testing for critical modules
\end{itemize}

\subsection*{Junior Backend Developer | MIB Promotions, Kuala Lumpur-Malaysia}
\textit{May 2024 – Present} \\
\begin{itemize}
    \item Designed and developed RESTful APIs using Django Rest Framework and FastAPI for web and mobile applications. 
    \item Built secure user authentication systems with JWT, OAuth2, and session-based logins
    \item Integrated external APIs including payment gateways and location services.
    \item Wrote unit tests, handled error log, and maintained clean modular codebases.
    \item Managed version control with Git and collaborated on GitHub with distributed teams.
    \item Developed and maintained back-end services on Heroku and PythonAnywhere.
    \item Used PostgreSQL for database design and complex query handling.\\

\end{itemize}

\section*{Education}
\textbf{MSc in Information Technology} \\
City University, Malaysia \\
\textit{2024 – Present}

\textbf{BSc in Computer Science Engineering} \\
City University of Bangladesh, Dhaka-Bangladesh \\
\textit{2012 – 2016}\\

\section*{Certifications}
\textbf{AI-Based Web Application with Python and Django} - Innovative skills BD \\
\textbf{Responsive Frontend Development with ReactJs} – Programming Hero \\

\section*{Projects}
\textbf{Hospital AI Chatbot System} – Developed a FAQ chatbot using NLP and FastAPI integrated into a Django admin dashboard. \\\\
\textbf{School Management Web App} - Built a full-scale school portal with Django backend and React front end with Tailwind UI. \\\\
\textbf{E-commerce Backend API} – Built a complete e-Commerce backend system using the Django Rest Framework with product management, cart system, orders, and JWT authentication. \\\\
\textbf{Blog API Service} – Created a lightweight blog engine back-end using the Django Rest Framework including CRUD functionality, user registration, and comments system. \\\\
\textbf{Healthcare Booking System} – Developed a FastAPI backend for a hospital appointment system with role-based access, scheduling, and REST endpoints. \\\\
\textbf{To-Do App API} – Built a simple task management back-end using the Django Rest Framework with user authentication, task CRUD operations and priority-based filtering.  \\


\end{document}
